---
title: "AR1_1mom"
output: html_document
date: '2022-08-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

SAMID = 'preVolcker_z2_EfiTest'
knitr::opts_chunk$set(echo = TRUE) # Whether to display the source code in the output document. 
PATHROOT <- 'C:/Users/22457561/OneDrive/UWA PhD/Fiscal_Monetary_Interaction/'
tryCatch({setwd(PATHROOT)},
         error = function(cond) { 
           PATHROOT <<- 'C:/Users/a1230166/OneDrive/UWA PhD/Fiscal_Monetary_Interaction/'
           setwd(PATHROOT)})
OUTFOLDER <- 'Results/'

library(tidyverse)
library(data.table)
library(readxl)
library(future)
library(furrr)
library(purrr)
library(sandwich) # HAC variance estimator
library(MTS)
library(DT)
library(plotly)
library(profvis)
library(tictoc)
# Plotting
library(gridExtra) # tableGrob
library(latex2exp) # TeX
source(str_c(PATHROOT, 'Codes/FunsMisc.R'))
source(str_c(PATHROOT, 'Codes/efisegri/sim_funs.R'))
```

## SIMULATION



```{r}
bigT = 1005
set.seed(12345)
u_ <- sim_ARCH1('u0'=0.2, 'u1'=0.6, 'T'=bigT)
y_ <- sim_AR3_hetero('alpha'=-0.25, 'rho1'=0.4, 'rho2'=0, 'rho3'=0, bigT, u_)[-(1:5)]

# Fit an AR1 in the mean and ARCH(1) in variance
#fGarch::garchFit(formula = ~arma(1,0)+garch(1,0), data=y_)
# Results from garchFit
##omega - the constant coefficient of the variance equation, by default 1e-6;
##alpha - the value or vector of autoregressive coefficients, by default 0.1, specifying a model #of order 1;
##beta - the value or vector of variance coefficients, by default 0.8, specifying a
#model of order 1;
##The optional values for the linear part are:
#mu - the mean value, by default 0;
#ar - the autoregressive ARMA coefficients, by default 0;
#ma - the moving average ARMA coefficients, by default 0

```

## ESTIMATION

## 2 moment equations, with nuisance parameter
### Moment conditions


$$
\begin{align}
\mathbb{E}\left[ (y_{t}- \color{cyan}{c_{1}} - \color{blue}{\rho} y_{t-1} ) y_{t-1}\right] &= 0 \\
\mathbb{E} \left[ ( u_{t}^{2} - \color{cyan}{c_2}- \color{blue}{\gamma} u_{t-1}^{2} ) \mathbf{z}_{t} \right] &= 0
\end{align}
$$

where $u_t = (y_t - \color{blue}{\rho} y_{t-1})$ and $y_{t-1}$ is the instrument ($z^{(1)}_{t}$). The first equation is the orthoganality condition for the conditional mean whereas the second equation is the orthoganlity condition for the forecasting error in the conditional variance: the forecasting error of the conditional variance should have a mean zero and being uncorrelated with previous values. 

$$
\mathbf{z}^{(2)}_{t} = 
\begin{bmatrix}
(y_{t-1} - \color{blue}{\rho} y_{t-2})^2
\end{bmatrix}
$$

### Manual moment functions
```{r}
# Moment conditions

theta0 <- c('rho1'=0.4, 'gamma'=0.6)
c1 = -0.25
Y1 <- cbind('y_t'= y_, 'y_tMinus1' = dplyr::lag(y_, n=1))[-(1), ]
u <- (Y1 %*% c(1, -theta0['rho1'])) - c1
#mean(u)


z1 <- cbind(1, Y1[, 'y_tMinus1'])
T = NROW(u)

FT1 <- (1/T)*t(z1) %*% u 


Y2 <-  cbind('uSq_t' = as.vector(u^2), 
             'uSq_tMinus1' = (as.vector(dplyr::lag(u, n = 1)))^2)[-(1), ]
c2 = 0.20
varUhat <- (Y2 %*% c(1, -theta0['gamma'])) - c2
#mean(varUhat)

z2 <- cbind(1, Y2[, 'uSq_tMinus1'])

FT2 <- (1/T)*t(z2) %*% varUhat

FT1
FT2

FT <- rbind(FT1,
      FT2)

(t(FT) %*% FT)


```

### Computing instruments and residuals
```{r}
this_uHat_fcn <- function(theta0, 
                          y_=y_, c1=-0.25, c2=0.20){
  Y1 <- cbind(y_, dplyr::lag(y_, n=1))[-(1), ]
  uMean <- {Y1 %*% c(1, -theta0['rho1']) - c1} %>%
            .[,1]
  
  Y2 <- (cbind(uMean, dplyr::lag(uMean, n = 1))[-(1), ])^2
  uVar <- {Y2 %*% c(1, -theta0['gamma']) - c2} %>%
        .[ , 1]
  
  Y <- rbind(cbind(Y1[-(1), ], matrix(0, nrow=NROW(Y2), ncol=NCOL(Y1))),
            cbind(matrix(0, nrow=NROW(Y2), ncol=NCOL(Y2)), Y2))
  
  uHat <- c(uMean[-(1)], # you lose another obs to compute lag of uMean_t
                uVar)
  # Instruments
  Z1 <- cbind(1, lag(y_, n=1))[-(1:2), ]
  Z2 <- cbind(1, lag(uMean^2, n=1))[-(1), ]
  
  Z <- rbind(cbind(Z1, matrix(0, nrow=NROW(Z1), ncol=NCOL(Z2))),
            cbind(matrix(0, nrow=NROW(Z2), ncol=NCOL(Z1)), Z2))
  NCOL(Z) == NCOL(Z1) + NCOL(Z2)
  
  list('Y'=Y, 'uHat'=uHat, 'Z'=Z)


}

# Returns a vector
get_b <- function(theta0) {
  matrix(c(1, 
           -theta0['rho1'],
           1,
           -theta0['gamma']),
         ncol=1)[,1]

}

```

### Set up initial objects

```{r}
T = NROW(y_) - 2
NEQUATIONS = 2
#X1 = rep(1, times=T) # thisis redudndant since im fixing c1
#X2 = rep(1, times=T)
#X <- rbind(cbind(X1, matrix(0, nrow=NROW(X1), ncol=NCOL(X1))),
#            cbind(matrix(0, nrow=NROW(X1), ncol=NCOL(X2)), X2))



NCORES = 1
STEPSPERCORE = 20
# Size of adjacent cells to explores is NCORES * STEPSPERCORE

PARAMS_CFG <- tribble(~name, ~iniVal, ~stepSize, ~minVal, ~maxVal,
                      'rho1',  0.5, 0.05, -1, 1,
                      'gamma',  0.9, 0.05, -1, 1)  %>%
              mutate('N_TICKS' = ((maxVal-minVal)/stepSize)+1)

theta0 <- c('rho1'=0.4, 'gamma'=0.5)
objs <- this_uHat_fcn(y_=y_, c1=-0.25, theta0=theta0)
Y <- objs$Y
#Yb <-  objs$Y %*% get_b(theta0)
Z <- objs$Z
uHat <- objs$uHat

# call efisegri
source(paste0(PATHROOT,'Codes/efisegri/efisegri_ND_fcns.R'))



```

### Search: first-stage
```{r}
thetaIni <- matrix(PARAMS_CFG$iniVal, ncol=1,
                     dimnames=list(PARAMS_CFG$name))[,1]
comp_S(THETA0=thetaIni, DATA=y_, UHAT_FCN=this_uHat_fcn)
#comp_S(c('beta1' = -0.51))
#comp_tests(c('beta1' = 0.5), NULL, Y,
#          Z, Ztrans, T, get_b)
minsS <- list('NelderMead' = NA)
              #'LBFGSB' = NA)
# 2-step GMM closed-form solution
#minsS$Closed <- first_Stage(method='Closed', SIV=stdIVobjs, WTlags = NULL)
minsS$NelderMead <- first_Stage(method='NelderMead', data=y_, uHat_fcn=this_uHat_fcn)
#m
```



