---
title: "2-moment equation"
output: html_document
date: '2022-07-27'
---

```{r initial_setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

SAMID = 'preVolcker_z2_EfiTest'
knitr::opts_chunk$set(echo = TRUE) # Whether to display the source code in the output document. 
PATHROOT <- 'C:/Users/22457561/OneDrive/UWA PhD/Fiscal_Monetary_Interaction/'
tryCatch({setwd(PATHROOT)},
         error = function(cond) { 
           PATHROOT <<- 'C:/Users/a1230166/OneDrive/UWA PhD/Fiscal_Monetary_Interaction/'
           setwd(PATHROOT)})
OUTFOLDER <- 'Results/'

library(tidyverse)
library(data.table)
library(readxl)
library(future)
library(furrr)
library(purrr)
library(sandwich) # HAC variance estimator
library(MTS)
library(DT)
library(plotly)
library(profvis)
library(tictoc)
# Plotting
library(gridExtra) # tableGrob
library(latex2exp) # TeX
source(str_c(PATHROOT, 'Codes/FunsMisc.R'))

```

## The model
2 indepenent AR processes:
$$
\begin{align}
y_{1, t} &= \alpha_{1,1} + \rho_{1,1} y_{1, t-1} + \rho_{1,2} y_{1, t-2} + \rho_{1,3} y_{1, t-3} + \varepsilon_1 \\ 
y_{2, t} &= \alpha_{2,1} + \rho_{2,1} y_{1, t-1} + \rho_{2,2} y_{1, t-2} +  \varepsilon_2 \\ 
\end{align}
$$
## Simulation
```{r}
sim_AR3 <- function(alpha, rho1, rho2, rho3, T) {
  epsilon_ <- rnorm(T)
  y_ <- rep(NA, times=T)
  y_[1] <- rho1*epsilon_[1]
  y_[2] <- rho2*epsilon_[2]
  y_[3] <- rho3*epsilon_[3]
  
  for (t in 4:T)
  {
    y_[t] <- alpha + rho1 * y_[t-1] + rho2 * y_[t-2] + rho3 * y_[t-3] + epsilon_[t]  
  }
  
  y_
  
}
set.seed(12345)

alpha1 = 0
alpha2 = 0
rho11 = 0.15
rho12 = -0.10
rho13 = 0.3
rho21 = -0.45
rho22= 0.15
y1 = sim_AR3(alpha1, rho11, rho12, rho13, 500)
y2 = sim_AR3(alpha2, rho21, rho22, 0, 500)

```

Simuated equations are:

$$
\begin{align}
y_{1, t} &= `r alpha1 ` + `r rho11` y_{1, t-1} + `r rho12` y_{1, t-2} + `r rho13` y_{1, t-3} + \varepsilon_1 \\ 
y_{2, t} &= `r alpha2` + `r rho21` y_{1, t-1} + `r rho22` y_{1, t-2} +  \varepsilon_2 \\ 
\end{align}
$$

## ESTIMATION

### GMM minimand
$$
\begin{align}
S_{T}(\theta) &= 
\underbrace{ \mathbf{f}^{\prime}}_{(1 \times K1+K2)} 
\; W \;
\underbrace{\mathbf{f}}_{(K1+K2 \times 1)} \\
S_{T}(\theta) &= \left( \mathbb{E}_{t} 
\begin{bmatrix}
\mathbf{z}_{1, t}^{\prime} u_{1, t} \\
\mathbf{z}_{2, t}^{\prime} u_{2, t} \\
\end{bmatrix} \right)^{\prime}
\; W \;
\mathbb{E}_{t} 
\begin{bmatrix}
\mathbf{z}_{1, t}^{\prime} u_{1, t} \\
\mathbf{z}_{2, t}^{\prime} u_{2, t} \\
\end{bmatrix} \\
\end{align}
$$

## Equations

### Residuals

$$
\begin{align}
u_{1, t} &= y_{1, t} - \alpha_{1,1} + \rho_{1,1} y_{1, t-1} + \rho_{1,2} y_{1, t-2} + \rho_{1,3} y_{1, t-3} \\ 
u_{2, t} &= y_{2, t} - \alpha_{2,1} + \rho_{2,1} y_{1, t-1} + \rho_{2,2} y_{1, t-2}  \\ 
\end{align}
$$
These can be conveniently rewritten in matrix form as
$$
U = Y \mathbf{b}(\theta) - X C
$$
with
$$
\underbrace{U}_{(2T \times 1)} \,=\,
\underbrace{\begin{bmatrix}
Y_1   &   0 \\
0   &   Y_2   \\
\end{bmatrix}}_{(2T \times )}
\underbrace{
\begin{bmatrix}
\mathbf{b}_1 \\
\mathbf{b}_2
\end{bmatrix}}_{( \times )}
\: - \:
\begin{bmatrix}
1   &   0 \\
1   &   0   \\
\vdots    &   \vdots \\
0   &   1   \\
0   &   1   \\
\end{bmatrix}_{(2T \times 2)}
\begin{bmatrix}
c_1 \\
c_2
\end{bmatrix}
$$
with

$$
\begin{align}
Y_{1} =
\begin{bmatrix}
y_{1,4} & y_{1,3} & y_{1,2} & y_{1,1} \\
y_{1,5} & y_{1,4} & y_{1,3} & y_{1,2} \\
\vdots & \vdots & \vdots & \vdots \\
y_{1,T} & y_{1,T-1} & y_{1,T-2} & y_{1,T-3} \\
\end{bmatrix}
\:,
\mathbf{b}_{1}(\theta_{1}) = 
\begin{bmatrix}
1 \\
\rho_{11} \\
\rho_{12} \\
\rho_{13} 
\end{bmatrix}
\:,
X_{1} = 
\begin{bmatrix}
1 \\
1 \\
\vdots \\
1
\end{bmatrix}_{(T \times 1)}
\end{align}
$$

### The moment conditions

$$
\begin{align}
\mathbf{z}_{1, t} &= \left[ y_{1, t-1}, y_{1, t-2}, y_{1, t-3} \right] \\
\mathbf{z}_{2, t} &= \left[ y_{2, t-1}, y_{2, t-2} \right] 
\end{align}
$$

$$
\begin{align}
\mathbf{f} =
\mathbb{E}_{t} 
\begin{bmatrix}
\mathbf{z}_{1, t}^{\prime} u_{1, t} \\
\mathbf{z}_{2, t}^{\prime} u_{2, t} \\
\end{bmatrix}
&=&
\begin{bmatrix}
  \begin{bmatrix} 
  y_{1, t-1} & y_{1, t-2} &  y_{1, t-3}  
  \end{bmatrix} 
  \left( y_{1, t} - \alpha_{1,1} + \rho_{1,1} y_{1, t-1} + \rho_{1,2} y_{1, t-2} + \rho_{1,3} y_{1, t-3} \right)
  \\
  \begin{bmatrix} 
  y_{2, t-1} & y_{2, t-2}   
  \end{bmatrix} 
  \left( y_{2, t} - \alpha_{2,1} + \rho_{2,1} y_{2, t-1} + \rho_{2,2} y_{2, t-2} \right)
\end{bmatrix}
\end{align}
$$
where the expectation is among observations (t). 
There are $K1$ instruments for the first equation and $K2$ for the second. The above moment conditions in matrix form are

$$
\underbrace{\mathbf{f}}_{(K_1+K_2 \times 1)} =
\begin{equation}
\left( \frac{1}{n} \right)
\underbrace{\begin{bmatrix}
Z_{1}^{\prime}    & 0    \\
0    & Z_{2}^{\prime}    \\
\end{bmatrix}}_{((K1+K2) \times 2T)}
\begin{bmatrix}
\mathbf{u_{1}} \\
\mathbf{u_{2}} 
\end{bmatrix}_{(2T \times 1)}
\end{equation}
$$

with,

$$
\begin{align}
Z_{1} = 
\begin{bmatrix}
z^{(k1)}_{1,t}    &   z^{(k2)}_{1,t}    &   z^{(k3)}_{1,t}    &   \cdots & z^{(K1)}_{1,t}   \\   
z^{(k1)}_{1,t+1}    &   z^{(k2)}_{1,t+1}    &   z^{(k3)}_{1,t+1}    &   \cdots & z^{(K1)}_{1,t+1}   \\
\vdots    &   \vdots    &   \vdots      &     \cdots    &   \vdots \\
z^{(k1)}_{1,T}    &   z^{(k2)}_{1,T}    &   z^{(k3)}_{1,T}    &   \cdots & z^{(K1)}_{1,T}   \\
\end{bmatrix}_{(T \times K1)} 
&
Z_{2} = 
\begin{bmatrix}
z^{(k1)}_{2,t}    &   z^{(k2)}_{2,t}    &   z^{(k3)}_{2,t}    &   \cdots & z^{(K2)}_{2,t}   \\   
z^{(k1)}_{2,t+1}    &   z^{(k2)}_{2,t+1}    &   z^{(k3)}_{2,t+1}    &   \cdots & z^{(K2)}_{2,t+1}   \\
\vdots    &   \vdots    &   \vdots      &     \cdots    &   \vdots \\
z^{(k1)}_{2,T}    &   z^{(k2)}_{2,T}    &   z^{(k3)}_{2,T}    &   \cdots & z^{(K2)}_{2,T}   \\
\end{bmatrix}_{(T \times K1)} \\
\end{align}
$$

### Build objects

```{r}
# Y %*% B
# Get the vector b
get_b <- function(theta0) {
  matrix(c(1, theta0['rho11'], theta0['rho12'], theta0['rho13'], 
                1, theta0['rho21'], theta0['rho22']), nrow=7, ncol=1)

}

get_deriv_B <- function(theta0) {
              DerivB <- rbind(c(0, 0, 0),
                          c(-1, 0, 0),
                          c(theta0['phiPi'], -(1-theta0['rhoR']), 0),
                          c(theta0['phiX'], 0, -(1-theta0['rhoR'])))
              colnames(DerivB) <- c('dfWRTrhoR', 'dfWRTphiPi', 'dfWRTphiX')
              
              DerivB
              
}


```
There are

```{r}
Y1 <- cbind(y1[4:NROW(y1)], y1[3:(NROW(y1)-1)], y1[2:(NROW(y1)-2)], y1[1:(NROW(y1)-3)])
head(Y1)
Y2 <- cbind(y1[4:NROW(y1)], y1[3:(NROW(y1)-1)], y1[2:(NROW(y1)-2)])
head(Y2)
NROW(Y2)
T = NROW(Y1)
Y <- rbind(cbind(Y1, matrix(0, nrow=NROW(Y2), ncol=NCOL(Y2))),
            cbind(matrix(0, nrow=NROW(Y1), ncol=NCOL(Y1)), Y2))
head(Y)

```


```{r }
Z1 <- cbind(dplyr::lag(y1, 1), dplyr::lag(y1, 2), dplyr::lag(y1, 3)) %>%
  .[-(1:3), ]
Z2 <- cbind(dplyr::lag(y1, 1), dplyr::lag(y1, 2)) %>%
  .[-(1:3), ]
T = NROW(Z1)
KZ1 = NCOL(Z1)
KZ2 = NCOL(Z2)

Z <- rbind(cbind(Z1, matrix(0, nrow=NROW(Z1), ncol=NCOL(Z2))),
            cbind(matrix(0, nrow=NROW(Z2), ncol=NCOL(Z1)), Z2))
NCOL(Z) == KZ1 + KZ2
NROW(Z) == 2*T

```

```{r X, eval=FALSE, include=FALSE}
X1 = rep(1, times=T) 
X2 = rep(1, times=T)
X <- rbind(cbind(X1, matrix(0, nrow=NROW(X1), ncol=NCOL(X1))),
            cbind(matrix(0, nrow=NROW(X1), ncol=NCOL(X2)), X2))

```

```{r search_settings}
NCORES = 1
STEPSPERCORE = 20
# Size of adjacent cells to explores is NCORES * STEPSPERCORE

NEQUATIONS = 2

PARAMS_CFG <- tribble(~name, ~iniVal, ~stepSize, ~minVal, ~maxVal,
                      'rho11',  NA, 0.05, -1, 1,
                      'rho12',  NA, 0.05, -1, 1,
                      'rho13',  NA, 0.05, -1, 1,
                      'rho21',  NA, 0.05, -1, 1,
                      'rho22',  NA, 0.05, -1, 1)  %>%
              mutate('N_TICKS' = ((maxVal-minVal)/stepSize)+1)


# Initial value
PARAMS_CFG$iniVal <- c('rho11' = 0.1, 'rho12' = 0.2, 'rho13' = 0.3,
            'rho21'= 0.01, 'rho22'=0.02)

  
#  as.data.frame(sam$Y) %>%
#  lm(R ~ 1 + R_tM1 + pi + x, data=.) %>%
#  .$coefficients %>%
#  {c('rhoR' = .[['R_tM1']], 
#     'phiPi' = .[['pi']],
#     'phiX' = .[['x']])}
  
# call efisegri
source(paste0(PATHROOT,'Codes/efisegri/efisegri_ND_fcns.R'))


```


#### Stage 1: find minimum

```{r debug}
alpha1 = 0.5
alpha2 = -0.7
rho11 = 0.15
rho12 = -0.10
rho13 = 0.3
rho21 = -0.45
rho22= 0.15

theta0 <- c('rho11' = 0.15, 'rho12' = -0.1, 'rho13' = 0.3,
            'rho21'= -0.45, 'rho22'=0.15)
comp_S(theta0)

sam <- tibble('y1_t' = y1,
              'y1_tM1' = lag(y1, n=1),
              'y1_tM2' = lag(y1, n=2),
              'y1_tM3' = lag(y1, n=3),
              'y2_t' = y2,
              'y2_tM1' = lag(y2, n=1),
              'y2_tM2' = lag(y2, n=2)) %>%
  {.[-(1:3), ]}

lm(y1_t ~ y1_tM1 + y1_tM2 + y1_tM3,
   data=sam) %>%
  summary()

lm(y2_t ~ y2_tM1 + y2_tM2,
   data=sam)

```

```{r Search, cache=TRUE}
# Find minimum and rotate initial value if needed it
# Standard IV objects
# Minimums S fcn (GMM minimand)
minsS <- list('NelderMead' = NA)
              #'LBFGSB' = NA)
# 2-step GMM closed-form solution
#minsS$Closed <- first_Stage(method='Closed', SIV=stdIVobjs, WTlags = NULL)
minsS$NelderMead <- first_Stage(method='NelderMead')
#minsS$LBFGSB <- first_Stage(method='LBFGSB', gr_T = comp_grad)

fstRes <- map2_dfr(minsS, names(minsS), 
                   function(minS, methodName) {
  list2env(minS, envir=environment())
  tibble('method' = methodName, 
         'rhoR' = par['rhoR'],
         'phiPi' = par['phiPi'],
         'phiX' = par['phiX'],
         'value' = value,
         'convergence' = convergence,
         'tSeconds' = tSeconds,
         'counts.function' = counts['function'],
         'counts.gradient' = counts['gradient'],
         'message' = message)
})

fstRes %>% 
        DT::datatable(filter='top',
                      options=list('scrollX'=TRUE))

```